---
title: "Constructing Hospital Score Using PCA"
author: "Seewoo"
date: '2020 5 30 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(skimr)
library(stringr)
library(recipes)
library(tidymodels)
```

# 1. EDA

### reading csv file

```{r read-data, include=FALSE}
table_1 <- read_csv('응급의료기관 기본정보 조회 서비스_1.csv')
table_2 <- read_csv('중증질환자 수용가능 정보_2.csv')
```

### merging plots
```{r}
hpdata <- inner_join(table_1, table_2, by='hpid')
```

### selecting variables
```{r}
hpdata <- hpdata %>%
  select(dutyName.x, starts_with('h'), starts_with('mk'))%>%
  select(-hv1, -hv12, -hvidate)
glimpse(hpdata)
str(hpdata)
```

### length of unique values in each variable
```{r}
nuniq <- c()
for(i in 1:length(colnames(hpdata))) {
  nuniq[i] <- hpdata[,i] %>%
  n_distinct()
}
nuniq
```

### remove columns with zero variance
```{r}
hpdata <- hpdata[,nuniq!=1]
```
```{r}
str(hpdata)
nuniq <- c()
for(i in 1:length(colnames(hpdata))) {
  nuniq[i] <- hpdata[,i] %>%
  n_distinct()
}
nuniq
```

### devide table
```{r}
hpdata_f <- hpdata[,nuniq<=3]
hpdata_n <- hpdata[,nuniq>3]
```



### recoding
```{r}
hpdata_f <- hpdata_f %>%
  mutate_all(funs(recode(., 'N1'=0L, '0'=0L, 'N'=0L, '1'=1L, 'Y'=1L, .default=1L)))
str(hpdata_f)
```

### merge again
```{r}
hpdata <- bind_cols(hpdata_n, hpdata_f)
glimpse(hpdata)
```

### centering and scaling
```{r}
hpdata_z <- hpdata %>%
  mutate_each_(funs(scale), vars=colnames(hpdata)[3:32])
head(hpdata_z[,3:32])
```


# 2. PCA

### Principal Component Analysis
```{r}
hp_without_id <- hpdata_z[,3:32] %>%
    as.matrix()
hp_pca <- prcomp(hp_without_id)
hp_pca[[1]]
hp_pca[[2]][,1:3]
```


### variance explained: \(R^2\)
First conponent explains 25% of the total variance.
```{r}
summary(hp_pca)
```


### scree plot
```{r}
screeplot(hp_pca, main = "", col = "blue", type = "lines", pch = 21)
```


### hospital score
```{r}
hp_pc1 <- predict(hp_pca)[,1]
hp_score <- (100-20*hp_pc1)
hospital_score <- hpdata %>%
  select(dutyName.x,hpid)%>%
  mutate(score=hp_score)
skim(hospital_score)
```


### plotting hospital scores
```{r}
library(ggplot2)
plot_score <- ggplot(hospital_score, aes(x=score))+
  geom_histogram(fill='sky blue', binwidth = 10)
plot_score
```

### exporting dataset
```{r}
write.csv(hospital_score, file = 'hospital_score')
```

### To Do 
* Exploratory Data Analysis
* Multicolinearity
* Variable selection
* Interpretation of each PC(constructing scores other than current hospital score)
  
  
  
  